Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:14	19:54:32	(Fri14.Aug)

\begin{figure}[tbhp]%\centering%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Steering within -3dB for each window}\label{windows_steering}
\end{figure}

@@

>>>>

\begin{figure}[tbhp]%\centering%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

@@

There is an upper bound to how much a window should be steered. Since each window's response is constrained to a unit gain in the look direction, each steered window's response is gained as shown in \Fig{window_steering}. moreUnder the constraint of a unit gain in the look direction, the effect of 
When steering the windows it is desirable to limit the amount of steering

Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.
